\begin{acknowledgement}

First and foremost, I would like to thank my advisor Henry Fuchs, who has guided me and supported me throughout my PhD career. 
I want to thank my committee members: David Luebke, Montek Singh, Leonard McMillan, Gordon Wetzstein, and Turner Whitted, for investing a lot of time and effort in guiding me along this PhD. 
Their brilliant ideas and useful suggestions often changed the course of my research for the better. 
Thanks Gordon for inspiring discussions, and for advising me on my occlusion paper, and later too. 

I want to thank my internship supervisors: Gordon Wetzstein, David Luebke, Kaan Aksit, Fu-Chung Huang, Josef Spjut, and Jaron Lanier for their fruitful collaboration, helpful discussions, and teaching me so many things about doing research and writing papers. 

Thanks to my research lab members Alex Blate, YoungWoon Cha, Praneeth Chakravarthula, David Dunn, Peter Lincoln, Andrew Maimone, Jim Mahaney, and Hanpeng Wang for a fun lab atmosphere and many helpful discussions. 

I want to thank my parents for their numerous sacrifices in ensuring an excellent education for me and instilling in me a strong set of values and principles. I offer my utmost love and appreciation to you. Thanks to Keshav for giving me a lifetime's worth of beautiful memories. I want to thank my wife, Anusha Lalitha, whose constant support, encouragement, and several visits while pursuing her own PhD across the country made this PhD possible. Your constant belief in me made all the difference. Thanks to Prasad uncle, Padmaja aunty, and Sameer for your kindness, understanding, and cheerful encouragement.

My graduate life has been memorable and enjoyable thanks to friends: Sridutt Balachandra, Srihari Pratapa, Atul Rungta, and many others. 

Also, thanks to the National Science Foundation and Intel for funding my PhD research. Thanks to Ronald Azuma and Greg Leeming from Intel for helpful discussions and feedback.

\end{acknowledgement}