%Acknowledgements are the author's statement of gratitude to and
%recognition of the people and institutions who helped the author's
%research and writing.

\begin{center}
\vspace*{52pt}
{\Large \textbf{ACKNOWLEDGEMENTS}}
\end{center}


First and foremost, I would like to thank my advisor Henry Fuchs, who has guided me and supported me through my PhD career. 
I want to thank my committee members: David Luebke, Montek Singh, Leonard McMillan, Gordon Wetzstein, and Turner Whitted, for investing a lot of time and effort in guiding me along this PhD. 
Their brilliant ideas and useful suggestions often changed the course of my research for the better. 
Thanks Gordon for inspiring discussions, and for advising me on my occlusion paper, and later too. 

I want to thank my internship supervisors: Gordon Wetzstein, David Luebke, Kaan Aksit, Fu-Chung Huang, Josef Spjut, and Jaron Lanier for their fruitful collaboration, helpful discussions, and teaching me so many things about doing research and writing papers. 

Thanks to my lab predecesors Andrew Maimone, Peter Lincoln, Alex Blate, Jim Mahaney, for a fun lab atmosphere, helpful discussions, and helping me get started in PhD research. I want to thank my co-authors of the \emph{Volumetric display} paper: Hanpeng Wang and Alex Blate, which forms a part of Chapter 3 of this dissertation.

I want to thank my parents for their emotional support, numerous sacrifices in ensuring an excellent education for me and instilling in me a strong set of values and principles. I offer my utmost love and appreciation to you. Thanks to Keshav for giving me a lifetime's worth of beautiful memories. 

I want to thank my wife, Anusha Lalitha, whose constant support, encouragement, and several visits while also pursuing a PhD across the country, made this PhD possible. Your constant belief in me made all the difference. Also, thanks to Prasad uncle, Padmaja aunty, and Sameer for your kindness, understanding, and encouragement.

I want to thank my UNC friends: Sridutt Balachandra, Praneeth Chakravarthula, David Dunn, Srihari Pratapa, Atul Rungta, and many others. 

Also, thanks to the National Science Foundation and Intel for funding my PhD research. Thanks for Ronald Azuma and Greg Leeming from Intel for helpful discussions and feedback.

\clearpage 
